Effects of pulsed hollow electron lens operation on the beam core in HL-LHC: \\First experimental studies and simulations.

### 2018-02-06 resex.tex
change abstract

\begin{abstract}
At the High Luminosity Large Hadron Collider (HL-LHC), a considerable amount of energy is expected to be stored in the beam tails due to the high beam intensity and, in addition, an overpopulation of the tails compared to a Gaussian distribution. To control and clean the tail population, the installation of two hollow electron lenses, one per beam, is presently under consideration. Beside the DC operation of the lenses, also pulsed operation is considered having the advantage to considerably increase the diffusion speed by exerting white or colored noise on the halo particles. In an ideal electron beam with azimuthal symmetry and no perturbations at the incoming and outgoing electron beam locations, only the halo particles are excited while leaving the core unperturbed. The picture though changes, if a residual field is present also at the location of the beam core exposing also the the particles in the center to noise. In this paper, we present first estimates of the residual field at the proton beam core expected from the HL-LHC hollow electron lens and summarize the results of the LHC experiments conducted in 2016 and 2017 to study the effects on the beam core in case of pulsed operation.
\end{abstract}

>>>>

\begin{abstract}
At the High Luminosity Large Hadron Collider (HL-LHC), a considerable amount of energy is expected to be stored in the beam tails due to the high beam intensity and, in addition, an overpopulation of the tails compared to a Gaussian distribution. To control and clean the tail population, the installation of two hollow electron lenses, one per beam, is presently under consideration. Beside the DC operation of the lenses, also pulsed operation is considered having the advantage to increase the diffusion speed by exerting white or colored noise on the halo particles. For an ideal electron lens, only the halo particles are excited while the core stays untouched. The picture though changes, if a residual field is present also at the location of the beam core exposing also the particles in the center to noise. In this paper, we present 
a summary of the LHC experiments conducted in 2016 and 2017 to study the effects on the beam core in case of pulsed operation, where uniform random noise and a resonant excitation were studied. In particular the resonant excitation features rich non-linear dynamics inducing unusual changes of the beam distribution and with it emittance and losses. These changes will be one of the main topics of this paper as they have not been observed and studied before in this detail. In addition to the presentation of the experimental and supportive simulation results, we also give first estimates of the residual field at the proton beam core expected from the HL-LHC hollow electron lens for comparison to the noise tolerances obtained in the experiments.
\end{abstract}
